Behavior Driven Development in Haskell

### 2012-05-28 paper.tex
Use (sort . sort) instead of (sort (sort ..))

\begin{quote}
\small
\begin{verbatim}
prop> \xs -> sort xs == sort (sort (xs::[Int]))
\end{verbatim}
\end{quote}

@@

\begin{quote}
\small
\begin{verbatim}
prop> sort xs == sort (sort (xs::[Int]))
\end{verbatim}
\end{quote}

@@

\begin{quote}
\small
\begin{verbatim}
Prelude Data.List> sort xs == sort (sort (xs::[Int]))
<interactive>:1:6: Not in scope: `xs'
<interactive>:1:24: Not in scope: `xs'
\end{verbatim}
\end{quote}

@@

\begin{quote}\small\begin{verbatim}
\xs -> sort xs == sort (sort (xs::[Int]))
\end{verbatim}\end{quote}

>>>>

\begin{quote}
\small
\begin{verbatim}
prop> \xs -> sort xs == (sort . sort) (xs :: [Int])
\end{verbatim}
\end{quote}

@@

\begin{quote}
\small
\begin{verbatim}
prop> sort xs == (sort . sort) (xs :: [Int])
\end{verbatim}
\end{quote}

@@

\begin{quote}
\small
\begin{verbatim}
Prelude Data.List> sort xs == (sort . sort) (xs :: [Int]))
<interactive>:1:6: Not in scope: `xs'
<interactive>:1:24: Not in scope: `xs'
\end{verbatim}
\end{quote}

@@

\begin{quote}\small\begin{verbatim}
\xs -> sort xs == (sort . sort) (xs :: [Int])
\end{verbatim}\end{quote}
